$p$-adic precision

### 2014-02-05 padicprec.tex
Paragraph "Lattices and computers" written

\todofor{Xavier}{Explain that if $E$ is finite dimensional and $K$ (and 
the absolute value is discrete), a lattice can be encoded by a finite 
amount of informations.}

@@

@@

\subsubsection*{Subresultants and B\'ezout coefficients}

>>>>

Although elements of $K$ are not representable in thein entirety on a 
computer, lattices in finite dimensional $K$-vector spaces are as soon 
as the elements of the quotient $B_K(1)/B_K(r)$ are for all $r \in 
(0,1)$. Indeed, given a lattice $L$ in $K^d$, there exists by definition 
two positive rational numbers $a$ and $b$ such that 
\begin{equation}
\label{eq:incllattice}
B_K(a)^d \subset L \subset B_K(b)^d.
\end{equation}
Moreover, a lattice $L$ satisfying \eqref{eq:incllattice} is uniquely 
determined by its image in the quotient $B_K(b)^d / B_K(a)^d \simeq 
(B_K(1)/B_K(r))^d$ with $r = \frac a b$. Therefore, the data of $L$ can 
be encoded by a $(d \times d)$ matrix with coefficients in $B_K(1)/
B_K(r)$. Thus, if elements in the latter ring are representable on a 
computer, so are the lattices $L$ for which Eq.~\eqref{eq:incllattice} 
holds. Finally, an arbitrary lattice $L$ in $K^d$ can be represented
by a triple $(a,b,M)$ where $a$ and $b$ satisfies \eqref{eq:incllattice}
and $M$ is a $(d \times d)$ matrix over $B_K(1)/B_K(\frac a b)$ 
representing the image of $L$ in $B_K(b)^d / B_K(a)^d$.

We furthermore remark that if $K = \Q_p$ (for some prime number $p$), 
the quotient $B_K(1)/B_K(r)$ is isomorphism to some $\Z/p^n\Z$ (with $n 
= \lfloor - \log_p r \rfloor$) are therefore is representable on a 
computer. Thus, the above discussion applies when $K = \Q_p$. Similarly 
it also applies when $K$ is a finite extension of $\Q_p$ or a field of
Laurent series with coefficients in a finite field.

@@

\todo{Explain how Newton polygons considered above behave under
usual operations (sum, multiplication and composition of functions).}

@@

\subsubsection*{Greatest common divisors and B\'ezout coefficients}
